\ttitle

### 2015-06-06 main.tex
Modified main.tex to include several package options for bibiblatex, including maxcitenames, mincitenames, uniquelist and uniquenames options - may need modification.
Added package /todo/ to main.tex
Changed todo to easy-todo package. Works

\usepackage[backend=biber,
			style=authoryear,
			url=false]{biblatex}
%For Square Brackets around citations
%http://tex.stackexchange.com/questions/16765/biblatex-author-year-square-brackets
\makeatletter

@@

\usepackage{graphicx}
\usepackage{caption} 
\usepackage{subcaption} % For Subfigures - not sure if I have used this anywhere
\usepackage{parskip} %Adds extra space between paragraphs
\usepackage{listings} %This is for the VBA code in the appendices
\usepackage{amsmath} %For aligning all equations on the equal to sign
\usepackage{pdfpages} %for including pdf files or individual pages of pdf files
\usepackage[pagewise]{lineno} %To help Donny review. Remove for final version
\linenumbers

@@

>>>>

\usepackage[backend=biber,
			citestyle=authoryear,
			bibstyle=authoryear,
			uniquelist=false,
			uniquename=false,
			maxcitenames=1,
			mincitenames=1,
			url=false]{biblatex}
%For Square Brackets around citations
%http://tex.stackexchange.com/questions/16765/biblatex-author-year-square-brackets
%http://ctan.mirrorcatalogs.com/macros/latex/contrib/biblatex/doc/biblatex.pdf - for info on all the above options. File is also stored in the Glasgow Research folder
\makeatletter

@@

\usepackage{graphicx}
\usepackage{caption} 
\usepackage{subcaption} % For Subfigures - not sure if I have used this anywhere
\usepackage{parskip} %Adds extra space between paragraphs
\usepackage{listings} %This is for the VBA code in the appendices
\usepackage{amsmath} %For aligning all equations on the equal to sign
\usepackage{pdfpages} %for including pdf files or individual pages of pdf files
\usepackage{easy-todo} %Adds todos to the document. Use [diable] as package option in final verion. Also see \listoftodos below.
\usepackage[pagewise]{lineno} %To help Donny review. Remove for final version
\linenumbers

@@

\listoftodos
